---
title: "p8105_hw1"
author: "Senna"
date: "2024-09-21"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Necessary packages and dataset are loaded. 
```{r, message = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

```{r include = FALSE}
# ??penguins
```
## Problem 1

The Penguins dataset contains size measurements for `r length(unique(penguins[["species"]]))` species of adult foraging penguins observed near Palmer Station, Antarctica. 

The size of the data set is `r nrow(penguins)` rows and `r ncol(penguins)` columns, in which the variables are: `r paste(names(penguins), collapse = ", ")`.

Three different species, `r paste(unique(penguins[["species"]]), collapse = ", ")` were observed in `r length(unique(penguins[["island"]]))` different islands. The sizes of the penguins were measured in terms of bills, flippers, and weight. The mean flipper length is `r round(mean(penguins[["flipper_length_mm"]], na.rm = TRUE), 3)`.  



```{r}
bill_flipper_plot <- ggplot(
  penguins, 
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length by Species",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)") 

print(bill_flipper_plot)

ggsave("flipper_vs_bill_scatterplot.png", plot = bill_flipper_plot)

```



## Problem 2  

Create a data frame as instructed.
```{r}
set.seed(123)
sample = rnorm(10)
log_vec = sample > 0 
char_vec = letters[1:10]
fac_vec = factor(rep(c("A", "B", "C"), length.out = 10))

p2df = tibble(
  sample = sample,
  log_vec = log_vec,
  char_vec = char_vec,
  fac_vec = fac_vec
)
```

Try to take the mean of each variable. 
```{r}
mean_sample = mean(pull(p2df, sample))
mean_log_vec = mean(pull(p2df, log_vec))
mean_char_vec = mean(pull (p2df, char_vec))
mean_fac_vec = mean(pull (p2df, fac_vec))
```
```{r, echo = FALSE}
cat(
  "Mean of random_sample:", mean_sample, "\n",
  "Mean of logical_vector:", mean_log_vec, "\n",
  "Mean of character_vector:", mean_char_vec, "\n",
  "Mean of factor_vector:", mean_fac_vec, "\n")

```

Taking the mean of random sample works because it has dlb, or double, as its data type. This is a type of numeric data, so the mean can be computed. 

Taking the mean of logic vector also works, since logical values can be coerced to numeric values (TRUE = 1, FALSE = 0).

However, taking the mean of character vector or factor vector does not work. Because they are not numeric data, and the mean() function cannot operate on them. 


```{r}
num_log = as.numeric(pull(p2df, log_vec))
num_char = as.numeric(pull(p2df, char_vec))
num_fac = as.numeric(pull(p2df, fac_vec))

```


```{r, echo = FALSE}
cat("Numeric logical vector:", num_log, "\n")
cat("Numeric character vector:", num_char, "\n")
cat("Numeric factor vector:", num_fac, "\n")

```

For logical vector, as.numeric() converts TRUE to 1 and FALSE to 0.
For the factor vector, as.numeric() assigns integers in order of the levels in the factor. 


