---
title: "p8105_hw1"
author: "Senna"
date: "2024-09-21"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Necessary packages and dataset are loaded. 
```{r, message = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

```{r include = FALSE}
# ??penguins

```

The Penguins dataset contains size measurements for `r length(unique(penguins[["species"]]))` species of adult foraging penguins observed near Palmer Station, Antarctica. 

The size of the data set is`r nrow(penguins)` rows and `r ncol(penguins)` columns, in which the columns (variables) are: `r paste(names(penguins), collapse = ", ")`.

Three different species, `r paste(unique(penguins[["species"]]), collapse = ", ")` were observed in `r length(unique(penguins[["island"]]))` different islands. The sizes of the penguins were measured in terms of bills, flippers, and weight. The mean flipper length is `r mean(penguins[["flipper_length_mm"]], na.rm = TRUE)`.  



```{r}
bill_flipper_plot <- ggplot(
  penguins, 
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length by Species",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)") +
  theme_minimal()

print(bill_flipper_plot)


ggsave("flipper_vs_bill_scatterplot.png", plot = bill_flipper_plot, width = 8, height = 6)

```



