---
title: "p8105_hw1"
author: "Senna"
date: "2024-09-21"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Necessary packages and dataset are loaded. 
```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

```{r eval=FALSE}
??penguins
```
The Penguins dataset contains size measurements for `r length(unique(penguins[["species"]]))` species of adult foraging penguins observed near Palmer Station, Antarctica. 

The variables of the dataset are `r paste(names(penguins), collapse = ", ")`.  


There are three species, `r paste(unique(penguins[["species"]]), collapse = ", ")`.  
There are `r length(unique(penguins[["island"]]))` different islands: `r paste(unique(penguins[["island"]]), collapse = ", ")`.  
Size of the dataset using nrow and ncol: `r nrow(penguins)` rows and `r ncol(penguins)` columns.  
The mean flipper length is `r mean(penguins[["flipper_length_mm"]], na.rm = TRUE)`.  


```{r}
p <- ggplot(
  penguins, 
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length by Species",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)") +
  theme_minimal()

print(p)


ggsave("flipper_vs_bill_scatterplot.png", plot = p, width = 8, height = 6)

```



